\documentclass[a4paper,10pt]{article}

\usepackage{geometry}
\usepackage{url}
\usepackage{hyperref}
\usepackage{tabularx}
% \usepackage[none]{hyphenat}
\usepackage{enumitem}
\usepackage{bookmark}
\usepackage{fancyhdr}

\geometry{
    includehead,
    % showframe,
    margin=0.69in,
    headheight=35pt
}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\renewcommand{\headrulewidth}{1pt}
\renewcommand{\footrulewidth}{0pt}

\setitemize{itemsep=0.1pt}
\setcounter{secnumdepth}{0}

\newcommand{\stackWidth}{0.8\textwidth}

\hypersetup{
colorlinks=true,
linkcolor=,
filecolor=magenta,
urlcolor=black,
}

\input{glyphtounicode}
\pdfgentounicode=1

\begin{document}

\fancyhead[L]{
    \Huge Jay Damani \\
    \normalsize Full Stack Developer
}

\fancyhead[C]{
}

\fancyhead[R]{
    Ahmadabad, Gujarat, India \\
    \href{mailto:jdamani@proton.me}{jdamani@proton.me} \\
    \href{tel:+91-9727587540}{+91-972-758-7540}
    % \faIcon{github}\href{https://github.com/jaydamani}{/jaydamani} \\
    % \faIcon{linkedin}\href{https://www.linkedin.com/in/damani-jay/}{/damani-jay}
}

\section{Summary}

Dedicated and detail-oriented developer with a passion for learning and
adapting to new technologies. Possessing three years of diverse experience in both professional and freelance capacities,
with a strong focus on collaborative teamwork and individual project dedication.
Actively contributed to open-source projects, showcasing the commitment to the developer community.

\section{Skills}

\begin{description}
    \item[Front End:] HTML5, CSS3, ReactJS, ReactNative, JQuery, Bootstrap
    \item[Back End:] NodeJS, Express, MongoDB, WatermelonDB, SQL Server, SQLite
    \item[Languages:] Javascript (ES6), Typescript, SQL, TSX, HTML VBScript, Tex
    \item[Concepts:] Object Oriented Programming, Functional Programming, Agile Methodologies
    \item[Miscellaneous:] Git, SVN, GitHub, Linux, Bash, ZSH, Regexp, SSMS, VS Code
\end{description}

\section{Experience}
\noindent
\textbf{StayinFront} \hfill Gandhinagar, Gujarat \\
Full Stack Developer \hfill August 2022--Present \
\begin{itemize}
    \item Built or improved various automated processes to import/export different data in CSV and JSON format, improving user productivity by 40\%.
    \item Developed an interactive dashboard with search and filters that helped users plan activities on weekly basis.
    \item Analyzed huge undocumented legacy codebase to assess its compatibility with unique client requirements, resulting in 70\% less technical debt.
    \item Utilized my code analysis to implement the given requirements without affecting existing functionalities, resulting in 60\% less bug reports.
    \item Earned the Most Valuable Player Award within my first year for overall excellent performance.
    \item Languages: HTML, CSS, JavaScript, SQL, VBScript
    \item Libraries/Tools: JQuery, BootStrap, SVN, ASP.NET
\end{itemize}

\section{Projects}
\begin{itemize}
    \item Developed discord bots using Typescript, NodeJS and Discord.JS demonstrating strong back-end skills.
    \item Creating a mobile wallet app using React Native, showcasing independent development skills.
    \item Contributed code to open-source projects, actively engaging with the developer community.
\end{itemize}

\section{Education}

\begin{description}
    \item[Bachelor of Science in Mathematics ] \hfill  \textbf{April 2023} \\
        Gujarat Arts and Science College, Ahmadabad
        \\ Total CGPA\@: 7.29
        % \item[Higher secondary education] % \hfill \textbf{March 2020} \\
        %     South International School
        %     \\ Total Percentage: 69\%
        % \item[Secondary education] % \hfill \textbf{March 2018} \\
        %     P.K Patel and U.D. Bhatt Secondary School
        %     \\ Total Percentage: 78\%
\end{description}

\section{Certificates}
\begin{description}
    \item[FreeCodeCamp]
        \href{https://www.freecodecamp.org/certification/jaydamani/javascript-algorithms-and-data-structures}{
            Javascript Algorithms and Data Structures
        }
    \item[FreeCodeCamp]
        \href{https://www.freecodecamp.org/certification/jaydamani/back-end-development-and-apis}{
            Back End Development and APIs (using NodeJS, Express and MongoDB)
        }
\end{description}

\end{document}
